### 2017-10-14 Sections/models_for_quantum_computation.tex
Added a few stubs and comments

\begin{figure}[!htb]
	\includegraphics[width=0.6\columnwidth]{cluster_state}
	\caption{Example of a \mbox{$4\times 3$} rectangular lattice cluster state. Each vertex in the graph represents a qubit initialised into \mbox{$\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$}. Edges represent the application of CZ gates between qubits (CZ gates commute, so the order is unimportant). Of sufficient dimension, states of this topology enable universal measurement-based quantum computation, whereby computation proceeds purely via single-qubit measurements, and all entangling operations have been commuted to the state preparation stage. Because CZ gates commute, the preparation of cluster states is time-independent, and easily implemented in a distributed or parallelised manner. The time-ordering of the single-qubit measurements is dependent on the structure of the graph and the algorithm.} \label{fig:cluster_state}
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.75\columnwidth]{cluster_state_circuit}
	\caption{Simple example of a cluster state that performs a computation comprising single-qubit operations and a CZ gate between two logical qubits. Let the two horizontal chains represent our two logical qubits. After inputting our input state from the left, we progressively measure out the cluster state qubits chronologically from left-to-right. Upon each single-qubit measurement, the choice of measurement basis teleports the action of a single-qubit gate. These accumulate sequentially. When we reach the point of measuring the two cluster state qubits joined with the vertical edge, the logical qubits accumulate the action of a CZ gate between them, since this is identically what that vertical edge physically corresponds to. Reaching the final two qubits, one from the upper rail and one from the lower, we obtain our two output logical qubits.} \label{fig:cluster_state_circuit}
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=\columnwidth]{cluster_identities} \index{Cluster state identities}
	\caption{Several cluster state identities. (a) a CZ gate between two qubits creates an edge between them in the graph. (b) Measurement of a qubit in the Pauli $\hat{Y}$ basis removes that qubit from the graph, while creating new edges between the neighbouring qubits. (c) Measurement of a qubit in the Pauli $\hat{Z}$ basis removes that qubit and any neighbouring edges.} \label{fig:cluster_ident} 
\end{figure}

When using non-deterministic gates to prepare cluster states, there are approaches to nonetheless preparing ideal cluster states. This is discussed in more detail in Sec.~\ref{sec:module}. Alternately, we can borrow ideas from percolation theory\index{Percolation theory} to simply tolerate defects in a cluster state lattice by working around them. Specifically, if the defect probability (i.e probability of a missing vertex or edge) is below some \textit{percolation threshold}\index{Percolation threshold}, \mbox{$p_\text{defect}\leq \epsilon_\text{threshold}$}, in the asymptotic limit we are guaranteed that routes exist through the lattice, enabling the required flow of information. This allows defective graphs to be employed for quantum computation.

@@

\begin{figure}[!htb]
	\includegraphics[width=\columnwidth]{toric_code}
	\caption{Graph representation of the toric QEC code, and its associated stabilisers. The star and plaquette stabilisers across all vertices, jointly specify the state of the graph up to two missing degrees of freedom, which encode a single logical qubit. Thus, a logical qubit is encoded jointly across the entire graph, not at any specific vertex. Logical operations are performed via operations following topological paths through the lattice (not shown). The graph may be distributed across multiple hosts for distributed quantum computation.} \label{fig:toric_code}
\end{figure}

>>>>

\begin{figure}[!htb]
	\includegraphics[width=0.3\textwidth]{cluster_state}
	\caption{Example of a \mbox{$4\times 3$} rectangular lattice cluster state. Each vertex in the graph represents a qubit initialised into \mbox{$\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$}. Edges represent the application of CZ gates between qubits (CZ gates commute, so the order is unimportant). Of sufficient dimension, states of this topology enable universal measurement-based quantum computation, whereby computation proceeds purely via single-qubit measurements, and all entangling operations have been commuted to the state preparation stage. Because CZ gates commute, the preparation of cluster states is time-independent, and easily implemented in a distributed or parallelised manner. The time-ordering of the single-qubit measurements is dependent on the structure of the graph and the algorithm.} \label{fig:cluster_state}
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.375\textwidth]{cluster_state_circuit}
	\caption{Simple example of a cluster state that performs a computation comprising single-qubit operations and a CZ gate between two logical qubits. Let the two horizontal chains represent our two logical qubits. After inputting our input state from the left, we progressively measure out the cluster state qubits chronologically from left-to-right. Upon each single-qubit measurement, the choice of measurement basis teleports the action of a single-qubit gate. These accumulate sequentially. When we reach the point of measuring the two cluster state qubits joined with the vertical edge, the logical qubits accumulate the action of a CZ gate between them, since this is identically what that vertical edge physically corresponds to. Reaching the final two qubits, one from the upper rail and one from the lower, we obtain our two output logical qubits.} \label{fig:cluster_state_circuit}
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{cluster_identities} \index{Cluster state identities}
	\caption{Several cluster state identities. (a) a CZ gate between two qubits creates an edge between them in the graph. (b) Measurement of a qubit in the Pauli $\hat{Y}$ basis removes that qubit from the graph, while creating new edges between the neighbouring qubits. (c) Measurement of a qubit in the Pauli $\hat{Z}$ basis removes that qubit and any neighbouring edges. \comment{Add X measurement identity}} \label{fig:cluster_ident} 
\end{figure}

%
% Non-Deterministic State Preparation
%

\subsubsection{Non-deterministic cluster state preparation}\index{Non-deterministic cluster staters preparation}

When using non-deterministic gates to prepare cluster states, there are approaches to nonetheless preparing ideal cluster states. There have been two main approaches that have become particularly well known.

The first is to use the ideas of \textit{micro-clusters}\index{Micro-clusters} and cluster state recycling\index{Cluster state recycling} to incrementally build up larger clusters, progressing as a random walk\index{Random walk}, which is biased in the direction of state growth. This approach is discussed in more detail in Sec.~\ref{sec:module}.

The second approach is to borrow ideas from percolation theory\index{Percolation theory} to simply tolerate defects in a cluster state lattice by working around them. Specifically, if the defect probability (i.e probability of a missing vertex or edge) is below some \textit{percolation threshold}\index{Percolation threshold}, \mbox{$p_\text{defect}\leq \epsilon_\text{threshold}$}, in the asymptotic limit we are guaranteed that routes exist through the lattice, enabling the required flow of information. This allows defective graphs to be employed for quantum computation.

%
% Percolation Theory Techniques
%

\paragraph{Percolation theory techniques} \index{Percolation theory}

%
% Error Teleportation
%

\paragraph{Error teleportation}\label{sec:cs_error_tele}\index{Error teleportation}

\cite{RohdeMunroEtal}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{toric_code}
	\caption{Graph representation of the toric QEC code, and its associated stabilisers. The star and plaquette stabilisers across all vertices, jointly specify the state of the graph up to two missing degrees of freedom, which encode a single logical qubit. Thus, a logical qubit is encoded jointly across the entire graph, not at any specific vertex. Logical operations are performed via operations following topological paths through the lattice (not shown). The graph may be distributed across multiple hosts for distributed quantum computation.} \label{fig:toric_code}
\end{figure}
